Optimized and Cost Considering Huffman Code For Biological Data Transmission

### 2015-01-20 Article/Article.tex

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
\journal{Nuclear Physics B}

\begin{document}

@@

\subsection{Huffman Code}
\subsection{Power Efficient on Data Transmission}
\subsection{Unequal Bit Considering On data Transmission}
\section{Approach}
\subsection{Proposed Scheme}
\subsection{Power Efficient Huffman code}
\subsection{Optimisation of the Codes}
\subsubsection{Problem formulation}
The problem of finding the best allocation of codes to each symbol can be   modelled as an Assignment Problems with Constraint, the problem is formulated as follows :\\\\
\textbf{Definition:} Given a set of codes $C=\left\{C_{1},C_{2}...C_{n}\right\}$, and a set of frequencies $C=\left\{Q_{1},Q_{2}...Q_{n}\right\}$. For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$ (cost of ones and zeros), the objective is to assign to each frequency a code in order to get the minimum total number of bits, while respecting the initial assignment total cost $S_{t}$.   
\\
The Objective Function is :

>>>>

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}
\journal{Nuclear Physics B}
\bibliographystyle{elsarticle-num}
\begin{document}

@@

\subsection{Huffman Code}
\subsection{Power Efficient on Data Transmission}
In the recent years, application of battery-powered portable devices, e.g. laptop computers and mobile phones has increased rapidly. Power dissipation has become a primary concern for digital community because it affects the performance,reliability, and the cost of computation         in both portable and non-portable devices. CMOS technologies were developed in order to reduce the power consumption in devices. Digital CMOS circuits have three major sources of power dissipation and are summarised in the following equation \cite{Weste88}:
\begin{equation}
\begin{split}
    P_{avg} ={}& P_{dynamic}+P_{short-circuit}+P_{leakage}\\
         ={}& \alpha_{0 \rightarrow 1}\cdot C_L\cdot V_{dd}^2\cdot f_{clk} + I_{sc}\cdot V_{dd}+I_{leakage}\cdot V_{dd}
\end{split}
\end{equation}
\subsection{Unequal Bit Considering On data Transmission}
\section{Approach}
\subsection{Proposed Scheme}
\subsection{Power Efficient Huffman code}
\subsection{Optimisation of the Codes}
\subsubsection{Problem formulation}
The problem of finding the best allocation of codes to each symbol can be   modelled as an Assignment Problems with Constraint, the problem is formulated as follows :\\\\
\textbf{Definition:} Given a set of codes $C=\left\{C_{1},C_{2}...C_{n}\right\}$, and a set of frequencies $C=\left\{Q_{1},Q_{2}...Q_{n}\right\}$. For each code we have the length of the code $|C_{i}|$ (number of bits) and the cost of the code $S_{C_{i}}$ (cost of ones and zeros), the objective is to assign to each frequency a code in order to get the minimum total number of bits, while respecting the initial assignment total cost $S_{t}$.   
\\
The Objective Function is :
